Generation of TypeScript Declaration Files from JavaScript Code

### 2020-08-26 programming-2021/main.tex
Correct email address. Simplified code example

\author{Fernando Cristiani}
\authorinfo{contact \email{fc@example.org}}
\affiliation{Hochschule Karlsruhe, Germany }

@@

Type aliases are expanded before the comparison and thus invisible to
\texttt{dts-compare}: the declaration
\lstinline{type T = string | number; declare function F(a: T);} is equivalent to
\lstinline{declare function F(a: string | number);}. The same approach applies to literal
interfaces. \texttt{dts-compare} does 
not contemplate differences in function return types, because interface inference of
function return types is not covered in the current version of \texttt{dts-generate}.

@@

\begin{figure}[tp]
  \centering
  \begin{subfigure}{0.80\linewidth}
    \begin{lstlisting}[language=TypeScript]
declare namespace gh {
  interface Options {
      enterprise?: boolean;
  }
  interface Result {
      user: string;
      repo: string;
      branch: string;
      https_url: string;
      tarball_url: string;
      clone_url: string;
      travis_url: string;
      api_url: string;
      zip_url: string;
  }
}

@@

export = gh;    
    \end{lstlisting}
    \caption{github-url-to-object/index.d.ts - DefinitelyTyped}
  \end{subfigure}

  \begin{subfigure}{0.80\linewidth}
    \begin{lstlisting}[language=TypeScript]
export = GithubUrlToObject;

@@

\begin{changethis}
  We exposed the fundamental aspect of capturing the developer's intention when inferring
  types in JavaScript. Instead of applying constraints and restrictions for operations
  with certain types, we presented a proposal that favors best practice. Uncommon usage is
  not forbidden but greatly discouraged. Accordingly, we collected evidence regarding the
  usage of JavaScript operators by analyzing 400 libraries.
\end{changethis}
% Finally, the architecture is composed of different blocks that interact with each
% other. Each block is independent and has a well defined behavior as well as clear input
% and output values. As a result, each block can be independently and simultaneously
% improved.

>>>>

\author{Fernando Cristiani}
\authorinfo{\email{fernando.cristiani@hs-karlsruhe.de}}
\affiliation{Hochschule Karlsruhe, Germany}

@@

Type aliases are expanded before the comparison and thus invisible to
\texttt{dts-compare}: the declaration
\lstinline{type T = string | number; declare function F(a: T);} is equivalent to
\lstinline{declare function} \lstinline{F(a: string | number);}. The same approach applies to literal
interfaces. \texttt{dts-compare} does 
not contemplate differences in function return types, because interface inference of
function return types is not covered in the current version of \texttt{dts-generate}.

@@

\begin{figure}[tp]
  \centering
  \begin{subfigure}{0.45\linewidth}
    \begin{lstlisting}[language=TypeScript]
declare namespace gh {
  interface Options {
      enterprise?: boolean;
  }
  interface Result {
      ...
  }
}

@@

export = gh;    
    \end{lstlisting}
    \caption{github-url-to-object/index.d.ts - DefinitelyTyped. Properties of interface \texttt{Result} were ignored for readability, since return types were not considered.}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.45\linewidth}
    \begin{lstlisting}[language=TypeScript]
export = GithubUrlToObject;

@@

% \begin{changethis}
%   We exposed the fundamental aspect of capturing the developer's intention when inferring
%   types in JavaScript. Instead of applying constraints and restrictions for operations
%   with certain types, we presented a proposal that favors best practice. Uncommon usage is
%   not forbidden but greatly discouraged. Accordingly, we collected evidence regarding the
%   usage of JavaScript operators by analyzing 400 libraries.
% \end{changethis}

% Finally, the architecture is composed of different blocks that interact with each
% other. Each block is independent and has a well defined behavior as well as clear input
% and output values. As a result, each block can be independently and simultaneously
% improved.
